Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-28 main-sketch.tex
fix mistake
typo
removed some figures

\noindent In the following whiskers-plots, the y-axis shows the
accuracy (or equivalently, the error) of the mechanisms.  Accuracy is
measured using Hellinger distance. The x-axis, instead shows one of
the previously mentioned independent variables --or a combination
thereof. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents our newly
designed exponential mechanism's behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the yellow box next to
it represents the performance of a variation of the basic Laplace
mechanism presented in Section (\ref{sec:base}) with the same
settings: that is $\epsilon, \delta$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

@@

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set sizing from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
    \label{subsubsec_vs_datasize1adir}
  }
  \subfigure[Data set sizing from $14000$ to $20000$]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichelt.eps}   
  \label{subsubsec_vs_datasize1bdir}} 
\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}

@@

\paragraph{Increasing dimensions and data size with balanced dataset}
\label{subsubsec_vs_dimension}
In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
of different sizes and different dimensions. The plot shows that
increasing the number of dimensions has a similar pejorative effect on
$\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
of dimensions and increasing the data size shows that the Laplace
mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
other words, dimensions have little influence on whether our
mechanisms will beat the Laplace mechanism.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
\label{fig_vs_dimension}
\end{figure}

\paragraph{Fixed data size and unbalaced datasets}
\label{subsubsec_vs_variance}
In Figure \ref{fig_vs_variance}, in the x-axis we considered different
levels of balance of the datasets. We study this variable only under
the two-dimensional $\betad$ distribution in order to be more
concise. The plot shows that $\hexpmech$ accuracy is better than the
one of Laplace when the dataset is balanced.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
\label{fig_vs_variance}
\end{figure}

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
We also considered balanced priors with increasing values in their dimensions.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

>>>>

\noindent In the following some of the plots show
mean error as a function of the datasize while others
are whiskers-plots where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows one of
the previously mentioned independent variables --or a combination
thereof. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents our newly
designed exponential mechanism's behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the yellow box next to
it represents the performance of a variation of the basic Laplace
mechanism presented in Section (\ref{sec:base}) with the same
settings: that is $\epsilon, \delta$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

@@

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
    \label{subsubsec_vs_datasize1adir}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
  \label{subsubsec_vs_datasize1bdir}} 
\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}

@@

% \paragraph{Increasing dimensions and data size with balanced dataset}
% \label{subsubsec_vs_dimension}
% In Figure \ref{fig_vs_dimension}, in the x-axis are observed data sets
% of different sizes and different dimensions. The plot shows that
% increasing the number of dimensions has a similar pejorative effect on
% $\hexpmech, \hexpmechd$, and the Laplace mechanism. Fixing the number
% of dimensions and increasing the data size shows that the Laplace
% mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. In
% other words, dimensions have little influence on whether our
% mechanisms will beat the Laplace mechanism.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
% \caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
% \label{fig_vs_dimension}
% \end{figure}

% \paragraph{Fixed data size and unbalaced datasets}
% \label{subsubsec_vs_variance}
% In Figure \ref{fig_vs_variance}, in the x-axis we considered different
% levels of balance of the datasets. We study this variable only under
% the two-dimensional $\betad$ distribution in order to be more
% concise. The plot shows that $\hexpmech$ accuracy is better than the
% one of Laplace when the dataset is balanced.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
% \caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
% \label{fig_vs_variance}
% \end{figure}

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
We also considered balanced priors with increasing values in their dimensions.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Observed data set is: $(5,5,5)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}
